Ising Sad paper

### 2019-05-20 papers/histogram/ising.tex
working on adding some text about methods to ising paper.

%The Wang-Landau approach thus has three parameters that need be
%specified: the factor by which to decrease $\gamma$ when flatness is
%acheived, the flatness criterion, and the cutoff that determines when
%the computation is complete.  In addition, an energy range (or in
%general, a \emph{set} of energies) must be supplied, so that the
%flatness criterion can be defined.

@@

\subsection{$1/t$-Wang-Landau}
1/t WL here.

\subsection{SAMC}
Stochastic Approximation Monte Carlo here.

\subsection{SAD Algorithm}\label{sec:sad}
Stochastic Approximation w/ Dynamic $\gamma$ here.

>>>>

@@

\subsection{$1/t$-Wang-Landau}
The $1/t$-WL method is a refinement of the original implementation that
addresses the error saturation of WL. Belardinelli and Pereyra
implemented a schedule~\cite{belardinelli2007fast} that enforced that
if $\gamma < \nicefrac{1}{t}$ then the update factor is set to
$\nicefrac{1}{t}$ and the histogram is no longer tracked. Using this
metric, the error saturation is avoided since the correct density of
states is approached asymptotically as
$t^{-\frac12}$~\cite{belardinelli2008analysis}. Zhou et. al also showed
that the WL algorithm never converges exponentially and succesfully
bounded the statistical error between $t^{-\frac12}$ and
$1/t$~\cite{zhou2008optimal}.

Schneider $\text{et. al}$ outlines minor refinements to the $1/t$-WL algorithm 
including $\nicefrac{N_S}{t}$ scaling and switching from standard WL to 
$1/t$-WL when the update factor $\gamma < 
\nicefrac{N_S}{t}$~\cite{schneider2017convergence}. As per the original 
$1/t$ implementation~\cite{belardinelli2007fast}, the update factor is 
decreased once all $N_S$ energy states are visited at least once (i.e. 
$H(E) \neq 0$) effectively avoiding the concept of `flatness'.  In this 
work, we refer to this refined algorithm as $1/t$-WL, with the update 
factor asymptoting to $\nicefrac{N_S}{t}$.

\subsection{SAMC}
The Stochastic Approximation Monte Carlo (SAMC) algorithm has a simple
schedule by which the update factor $\gamma$ is continuously
decreased~\cite{liang2007stochastic, werlich2015stochastic,
schneider2017convergence}.  The update factor is defined in the
original implementation~\cite{liang2007stochastic} in terms of an
arbitrary tunable parameter $t_0$,
\begin{align}
\gamma_{t}^{\text{SA}} =\frac{t_0}{\max(t_0,t)}
\end{align}
where as above $t$ is the number of moves that have been attempted.
SAMC offers extreme simplicity and proven convergence.
Provided the update factor satisfies
\begin{align}
\sum_{t=1}^\infty \gamma_{t} = \infty \quad\textrm{and}\quad
\sum_{t=1}^\infty \gamma_{t}^\zeta < \infty
\end{align}
where $\zeta \in \{1,2\}$, Liang has shown that the weights are proven
to converge to the true density of states~\cite{liang2006theory,
liang2007stochastic}.  Unlike WL methods, the energy range need not be
known \emph{a priori.}  The convergenc time depends only on the choice of
parameter $t_0$.  Liang \emph{et al.} give a rule of thumb in
which $t_0$ is chosen in the range from $2N_S$ to $100N_S$ where $N_S$
is the number of energy bins~\cite{liang2007stochastic}.  Schneider
\emph{et al.} found that for the Ising model this heuristic is helpful
for small spin systems, but that larger systems require an even higher
$t_0$ value~\cite{schneider2017convergence}.

\subsection{SAD Algorithm}\label{sec:sad}
In our previous work we discuss this in detail so here we only highlight...
Stochastic Approximation w/ Dynamic $\gamma$ here.
